How to obtain the redshift distribution from probabilistic redshift estimates

### 2018-01-18 research/paper/draft.tex
updated abstract

\author{Alex Malz\altaffilmark{1}, David W. Hogg\altaffilmark{1,2,3,4}, Phil 
Marshall\altaffilmark{5}, \& Others}
\email{aimalz@nyu.edu}

@@

\begin{abstract}
The redshift distribution $n(z)$ is a crucial ingredient for weak lensing 
cosmology.  Spectroscopically confirmed redshifts for the dim and numerous 
galaxies observed by weak lensing surveys are expected to be inaccessible, 
making photometric redshifts (photo-$z$s) the next best alternative.  Because 
of the nontrivial inference involved in their determination, photo-$z$ point 
estimates are being superseded by photo-$z$ probability distribution functions 
(PDFs).  However, analytic methods for utilizing these new data products in 
cosmological inference are still evolving.  This paper presents a novel 
approach to estimating the posterior distribution over $n(z)$ from a survey of 
galaxy photo-$z$ PDFs based upon a probabilistic graphical model of 
hierarchical inference.  We present the Cosmological Hierarchical Inference 
with Probabilistic Photometric Redshifts (\chippr) code implementing this 
technique, as well as its validation on mock data and testing on the 
\texttt{Buzzard} simulations.  \chippr yields a more accurate characterization 
of $n(z)$ containing information beyond the best-fit estimator produced by 
traditional procedures.  The publicly available code is easily extensible to 
other one-point statistics that depend on redshift.

@@

\keywords{catalogs --- cosmology: cosmological parameters --- galaxies: 
statistics --- gravitational lensing: weak --- methods: analytical --- methods: 
data analysis --- methods: statistical --- techniques: photometric}

@@

The tests presented here are conducted with samples of $N = 10^{4}$ with

@@

In comparison with use of the stacked estimator of the redshift distribution 
function, the hierarchical approach is computationally expensive.  In a future 
revision, the \chippr code will be optimized for speed and resource efficiency. 
 At this stage, we establish scaling behavior to project the expense in terms 
of computational resources.

@@

\begin{acknowledgements}
AIM thanks Mohammadjavad Vakili for insightful input on statistics, Geoffrey 
Ryan for assistance in debugging, and Boris Leistedt for helpful comments 
provided in the preparation of this paper.
\end{acknowledgements}

>>>>

\author{Alex Malz\altaffilmark{1}, David W. Hogg\altaffilmark{1,2,3,4}, Phil 
Marshall\altaffilmark{5}}
\email{aimalz@nyu.edu}

@@

\begin{abstract}
A trustworthy estimate of the redshift distribution $n(z)$ is crucial for weak 
lensing cosmology.  Spectroscopically confirmed redshifts for the dim and 
numerous galaxies of weak lensing surveys are expected to be inaccessible, 
making photometric redshifts (photo-$z$s) the next best alternative.  The 
nontrivial systematics affecting photo-$z$ estimation have motivated the weak 
lensing community to favor photo-$z$ probability distribution functions (PDFs) 
as a more comprehensive alternative to photo-$z$ point estimates.  However, 
analytic methods for utilizing these new data products in cosmological 
inference are still evolving.  This paper presents the Cosmological 
Hierarchical Inference with Probabilistic Photometric Redshifts (CHIPPR) model, 
a novel approach to estimating the $n(z)$ from a catalog of galaxy photo-$z$ 
PDFs based upon a probabilistic graphical model of hierarchical inference.  We 
present the publicly available \chippr code implementing this technique, as 
well as its validation on mock data.  The CHIPPR model yields a more accurate 
characterization of $n(z)$ containing information beyond the best-fit estimator 
produced by traditional procedures.

@@

\keywords{cosmology: cosmological parameters --- galaxies: statistics --- 
gravitational lensing: weak --- methods: data analysis --- methods: statistical}

@@

@@

@@

\begin{acknowledgements}
AIM thanks Elisabeth Krause for assistance with the \texttt{CosmoLike} code, 
Mohammadjavad Vakili for insightful input on statistics, Geoffrey Ryan for 
advice on debugging, and Boris Leistedt for helpful comments provided in the 
preparation of this paper.
\end{acknowledgements}
